---
output:
  pdf_document: default
  html_document: default
---
# METHODS

```{r setup, include = FALSE}
# load R libraries here; the `include` flag in the chunk options above tells
# whether to print the results or not. Usually you don't want to print the
# library statements, or any code on the pdf.

# Main Packages ========
# I use these in every doc
library(tidyverse)
library(knitr)
library(kableExtra)
library(modelsummary)

options(dplyr.summarise.inform = FALSE)

# Other packages ------
# These sometimes get used, and sometimes don't.
library(mlogit)

# Load functions ------
source("R/functions.R")

# Instructions and options =========
# prints missing data in tables as blank space
options(knitr.kable.NA = '') 
# tells kableExtra to not load latex table packages in the chunk output
options(kableExtra.latex.load_packages = FALSE) 

# round and format numbers that get printed in the text of the article.
inline_hook <- function(x) {
  if (is.numeric(x)) {
    format(x, digits = 3, big.mark = ",")
  } else x
}
knitr::knit_hooks$set(inline = inline_hook)

knitr::opts_chunk$set(
  #tab.width = 7.5,
  #tab.asp = 0.8,
  #out.width = "60%",
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE
)
# options for latex-only output
if(knitr::is_latex_output()) {
  knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
} 

```

Pearson correlation factors were calculated to determine correlation to crash severity in this study. Equation \@ref(eq:pearson) shows how to calculate Pearson correlation given two potentially correlated variables, X and Y, using covariance. 

\begin{equation}
  \rho = \frac{\text{cov}(X,Y)}{\sigma_x \sigma_y}
  (\#eq:pearson)
\end{equation}

<!-- make it clearer that this paragraph is about both segments and intersections -->
<!-- The segmentation method used in this model is based on characteristics like AADT and length to facilitate homogeneous segments. Intersection related crashes were determined by estimating the location of the stop bar given approach speeds. Considering that the segments and intersection are homogeneous and consistent, it is possible to calculate correlation between crash severities and other factors.  -->

Manner of collision variables and pedestrian related variables were compared to crash severity to determine correlation factors. The pedestrian related variables used here are involvment of pedestrians, pedacycle, or motorcycles in the crash as well as the presence or number of schools or transit stops within 1000 feet of the crash. The resulting correlation factors for manner of collision are shown in Table \@ref(tab:Manner) and the correlation factors for pedestrian variables are shown in Table \@ref(tab:Ped). These correlation factors were evaluated at intersections and roadway segments separately to ensure homogeneity of roadway characteristics at crash locations.

```{r Manner}
# Correlation for Manner of Collision ######################################

df <- read_csv("data/CAMS_Crashes_14-21.csv")
df <- corrManner(df,SEG_ID)
df2 <- read_csv("data/ISAM_Crashes_14-21.csv")
df2 <- corrManner(df2,INT_ID)
makeTable(df, df2, "Correlation Matrix for Crash Severity and Manner of Collision")

```

```{r Ped}
# Correlation for Manner of Collision ######################################

df <- read_csv("data/CAMS_Crashes_Compiled_14-21_fixed.csv")
df <- corrPedCAMS(df,SEG_ID)
df2 <- read_csv("data/ISAM_Crashes_14-21_extra.csv")
df2 <- corrPed(df2,INT_ID)
makeTable(df, df2, "Correlation Matrix for Crash Severity and Pedestrain Variables")

```

Crash data for this analysis were retrieved from the Utah Department of Transportation (UDOT) through police reports, and roadway data from the UDOT open data portal were used to identify intersections and segments on state routes. Data about the number of transit stops came from the Utah Transit Authority (UTA) and data about the number of schools came from the Utah Geospatial Resource Center (UGRC). 